% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=6.0in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font



\begin{document} 
 
\name{Mitchell Goudy\\[12pt]} % the \\[12pt] adds a blank line after name

\address{  mitchell.a.goudy@gmail.com \\ mitchellgoudy.com \\ https://github.com/mgoudy91 \\ }

\address{ (720) 480-7126 \\ 2119 Spruce Street \#3 \\ Boulder, CO 80302 }

\begin{resume} 
 
\section{Objective} 
  I am a focused Software Engineer, Web Developer, and Designer, that cares deeply about my work as well as how I can improve myself professionally. 

 % Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Skills}
   \begin{tabular}{l p{5.0in}}
    {Languages:} & JavaScript, Ruby (Rails), HTML, CSS (SCSS), MySQL, PostgreSQL, Java, C, C++, PHP, XML, LaTeX \\ [0.5ex]
    {Libraries:} & jQuery, AJAX, Google Maps, Liquid, Angular.js, Android (ADK), openGL, webGL \\ [0.5ex]
    {Software:} & Sublime Text, Bash/Unix Shells, Git/Hg, mySQL Workbench, Photoshop/GIMP, WinSCP, VirtualBox, Eclipse, InDesign, JIRA \\ [0.5ex]
    {OS:} & Linux (Ubuntu), Windows (8, 7, Vista, XP), OS X \\ [0.5ex]
   \end{tabular}

\section{Experience}
 {\bf Web Developer,} Dolphin Micro, Louisville, CO  \hfill May 2013 - November 2013
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Website and application development and design.
 \item Worked in both team and solo settings to design, implement, test, and maintain websites and applications for a wide clientele base.
 \item Handled simultaneous projects with various teams, deadlines, and requirements
 \item Worked on many high-profile contracts such as AT\&T and Old Navy.
 \item Rails, JavaScript, jQuery, RSpec, CSS (SCSS), HTML, MySQL stack.
 \end{itemize}

 {\bf Intern,} Connextions, Broomfield, CO  \hfill December 2011 - December 2012
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Web app development, front-end design and development, and back-end process management.
 \item Created pharmacy-finding tool using JavaScript and Google Maps API. 
 \item Wrote and maintained HIPAA-compliant code that utilized actual insurance provider and patient data.
 \item Worked in Groovy, Grails, HTML, JavaScript, jQuery, AJAX, and in-house visual process modeler.
 \end{itemize}

 {\bf Intern,} FirstBank, Lakewood, CO  \hfill May 2011 - August 2011
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Web development and design, and QA / testing.
 \item Created and updated pages and features, as well as designed banners and graphics for company web presence.
 \item Worked in JavaScript, jQuery, Dreamweaver, Photoshop.
 \end{itemize}

 {\bf Intern,} InfoNow, Denver, CO  \hfill May 2010 - August 2010
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Created time-tracking portlet extension to JIRA for internal employee work-logging and issue tracking.
 \item Worked in Java, JavaScript, XML, .NET, and AJAX. 
 \end{itemize}

\section{Education} 
  BS of Computer Science from University of Colorado Boulder, (2010 - 2013)\\
  GPA 3.8, Software Engineering focus \\
  Senior Project
  \begin{itemize} \itemsep -2pt  % reduce space between items
  \item NASA/LASP project
  \item webGL web application and visualizer for the MMS project
  \item Worked in JavaScript, webGL, XML, and python
  \end{itemize}  

\section{Awards}
  \begin{itemize} \itemsep -12pt \setlength{\itemindent}{-15pt}
  \item CU Dean’s List (2010-2013) \\
  \item Miami University Dean’s List (2009-2010) \\
  \item CU Mobile App Challenge 3rd Place (2013) \\
  \item Tau Beta Pi Engineering Honor Society Member and Officer (2010-2013) \\
  \end{itemize}

\end{resume} 
\end{document} 



